---
title: "Errata"
subtitle: "On Barari, Coppock, Graham and Padgett (2024), *Public Opinion Quarterly* 88(4)"
format:
  pdf:
    output-file: barari_etal_2024_errata.pdf
    geometry: margin=1.25in
    fontsize: 11pt
    include-in-header:
      text: |
        \usepackage{caption}
        \captionsetup{labelformat=empty}
        \usepackage{float}
        \floatplacement{table}{H}
        \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
here::i_am("errata.qmd")

t2 <- read_csv(here("maintained", "output", "table_2_avg_effect_by_primary.csv"),
               show_col_types = FALSE)
txt <- read_csv(here("maintained", "output", "text_sample_and_weighting.csv"),
                show_col_types = FALSE)
fig1 <- read_csv(here("maintained", "output", "figure_1_thresholds_by_primary.csv"),
                 show_col_types = FALSE)

cell <- function(topic_key, party_name, quantity) {
  rows <- str_detect(t2$Topic, fixed(topic_key)) & t2$Party == party_name
  stopifnot(sum(rows) == 1)
  t2[[quantity]][which(rows)]
}

group_n <- function(quantity_name) {
  value <- txt$value[txt$quantity == quantity_name]
  stopifnot(length(value) == 1)
  formatC(value, format = "d", big.mark = ",")
}

# The change-format share of a group saying more or less likely, as the panel plots it.
panel_share <- function(group, sign_value) {
  rows <- fig1$primary_party == group & fig1$topic == "docs" & fig1$sign == sign_value &
    str_trim(fig1$measure) == "Change" & fig1$threshold == -0.01
  stopifnot(sum(rows) == 1)
  sprintf("%.1f", 100 * fig1$P[which(rows)])
}

pp <- function(x) sprintf("%.1f", x)
pv <- function(x) sprintf("%.3f", x)
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from this tibble into
# this document and into the machine-readable errata_entries.csv written at the bottom of
# the file, which is what any other document carrying these corrections reads. Before the
# spine existed an entry was written out in prose wherever it was needed, and the copies
# had already diverged.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here. Nothing else in a field is markup, so the same string can be set by any of them.
#
# Numbering is the published note's and is APPEND-ONLY: entry 2 can already have been cited,
# so a later finding is added at the end and never interleaved.
#
# A published or corrected value that the pipeline computes stays computed: the field is
# built with str_glue() so the number is produced when this document renders, not typed.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note,

  1, "float", "pipeline", "full",
  "Figure 1's panels are printed in the wrong order",
  "published figure 1 caption, p. 1224",
  "Figure 1a displays results for respondents who did not plan to vote in either primary (N = 754). [[Figure 1b]] and [[1c]] displays results for those who plan to vote in the Republican primary (N = 2,026) and Democratic primary (N = 1,953).",
  "[[figure 1 is reprinted below]] with its panels in the order the caption and the body text describe. Nothing plotted differs.",
  str_glue(
    "The panel printed as **(b)** is the Democratic one. Its belief column shows ",
    "{panel_share('Democratic', 1)} per cent of respondents saying more likely against ",
    "{panel_share('Democratic', -1)} per cent saying less likely, and its vote column is the ",
    "general election, which only respondents outside the Republican primary were asked ",
    "about. The panel printed as **(c)** is the Republican one, with a belief split of ",
    "{panel_share('Republican', 1)} per cent more likely against ",
    "{panel_share('Republican', -1)} per cent less likely and a Republican primary vote ",
    "column. The body text carries the same assignment as the caption and so points at the ",
    "wrong panel twice, at \"In figure 1b, huge fractions of Republican primary voters report ",
    "that the indictment made them think it was 'less likely' Trump mishandled documents\" ",
    "and at \"We see this same basic pattern (reversed) among Democratic primary voters in ",
    "figure 1c.\""),

  2, "quantity", "pipeline", "full",
  "The counterfactual estimates for respondents intending neither primary",
  "published p. 1222",
  "By contrast, the counterfactual format suggests indifference: these respondents report that the indictment slightly revised their beliefs in favor of the idea that Trump mishandled documents ([[+1.8]] pp, s.e. = 0.9, [[p = 0.05]]), with no substantial effect on vote choice ([[+0.1]] pp, s.e. = 0.9, [[p = 0.89]]).",
  str_glue("By contrast, the counterfactual format suggests indifference: these respondents report that the indictment slightly revised their beliefs in favor of the idea that Trump mishandled documents ([[+{pp(cell('Believe', 'Neither', 'cf_diff'))}]] pp, s.e. = 0.9, [[p = {pv(cell('Believe', 'Neither', 'cf_p'))}]]), with no substantial effect on vote choice ([[+{pp(cell('general election', 'Neither', 'cf_diff'))}]] pp, s.e. = {pp(cell('general election', 'Neither', 'cf_se'))}, [[p = {pv(cell('general election', 'Neither', 'cf_p'))}]])."),
  paste("Table 2 already prints all four corrected values. The two standard errors quoted in",
        "the sentence are right, so the estimates were not computed on a different sample; the",
        "four wrong figures appear only here."),

  3, "quantity", "pipeline", "full",
  "The p-value for the effect on Republican primary vote",
  "published p. 1222",
  "Republican primary voters also thought that the indictment made them less likely to vote for Trump in the primary: on average, they reported a 64.1 percent chance of doing so, compared with 65.7 percent if the indictment had not been issued (difference = 1.6 pp, s.e. = 0.6, [[p = 0.02]]).",
  str_glue("Republican primary voters also thought that the indictment made them less likely to vote for Trump in the primary: on average, they reported a 64.1 percent chance of doing so, compared with 65.7 percent if the indictment had not been issued (difference = 1.6 pp, s.e. = 0.6, [[p = {pv(cell('primary election', 'Republican', 'cf_p'))}]])."),
  str_glue(
    "Table 2 prints {pv(cell('primary election', 'Republican', 'cf_p'))} for the same ",
    "estimate. The estimate and its standard error are stated correctly, and the finding is ",
    "significant at conventional levels on either figure."),

  4, "quantity", "pipeline", "full",
  "Figure 1's caption reports the wrong group sizes",
  "published figure 1 caption, p. 1224",
  "Figure 1a displays results for respondents who did not plan to vote in either primary (N = [[754]]). Figure 1b and 1c displays results for those who plan to vote in the Republican primary (N = [[2,026]]) and Democratic primary (N = [[1,953]]).",
  str_glue("Figure 1a displays results for respondents who did not plan to vote in either primary (N = [[{group_n('n_primary_neither')}]]). Figure 1b and 1c displays results for those who plan to vote in the Republican primary (N = [[{group_n('n_primary_republican')}]]) and Democratic primary (N = [[{group_n('n_primary_democratic')}]])."),
  str_glue(
    "The three published figures are the counts of respondents by partisan identity, not by ",
    "intended primary: {group_n('n_party_id_independent')} respondents identify as ",
    "Independents, {group_n('n_party_id_republican')} as Republicans and ",
    "{group_n('n_party_id_democrat')} as Democrats. They are the group sizes of figure A.1.")
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The prose below counts the entries in words, as the note has always done.
n_entries_word <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
                    "ten", "eleven", "twelve")[nrow(entries)]

# The spine's markup, resolved for this document.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
```

This note lists `r n_entries_word` errors in "Did Trump's Indictments Rally His Base? Evidence from the Counterfactual Format," published in *Public Opinion Quarterly* 88(4), doi [10.1093/poq/nfae061](https://doi.org/10.1093/poq/nfae061). **None of them changes a conclusion of the paper.** They are recorded because a reader who followed the text to a panel, or quoted one of the numbers, would be misled.

Item 1 is a figure whose panels are printed in an order the caption and the body text do not describe. Items 2 and 3 are sentences that disagree with the article's own table 2. Item 4 is a caption reporting the wrong group sizes. Every corrected value below is computed from the deposited replication archive ([10.7910/DVN/QDOBJF](https://doi.org/10.7910/DVN/QDOBJF)) at the time this document is rendered. The maintained code is at [github.com/active-maintenance-aec/barari_etal_2024](https://github.com/active-maintenance-aec/barari_etal_2024).

```{r entry-1, results="asis"}
# A heading is only a heading when a blank line precedes it, so every emitted entry opens
# with one. This entry's corrected artifact is the float printed beneath it rather than a
# token, so its corrected field is set as a sentence and its markers are stripped.
e <- entries |> filter(entry == 1)
cat("\n\n## 1. ", e$title, "\n\nPublished, ", str_remove(e$location, "^published "), ":\n\n> ",
    bold(e$published), "\n\n", e$note, "\n\nCorrected: ",
    str_remove_all(e$corrected, "\\[\\[|\\]\\]"), "\n", sep = "")
```

```{r fig-1a}
#| out-width: 100%
#| fig-align: center
#| fig-cap: "(a) Respondents who did not plan to vote in either primary"
knitr::include_graphics("maintained/output/figure_1a_thresholds_neither.pdf")
```

```{r fig-1b}
#| out-width: 100%
#| fig-align: center
#| fig-cap: "(b) Respondents who plan to vote in the Republican primary"
knitr::include_graphics("maintained/output/figure_1c_thresholds_republican.pdf")
```

```{r fig-1c}
#| out-width: 100%
#| fig-align: center
#| fig-cap: "(c) Respondents who plan to vote in the Democratic primary"
knitr::include_graphics("maintained/output/figure_1b_thresholds_democratic.pdf")
```

\parbox{\linewidth}{\footnotesize\raggedright \textit{Note:} Figure 1 as published, with the panels reordered to match the caption and the body text. Every plotted proportion is unchanged. Drawn from the deposited replication archive by \texttt{maintained/figure\_1\_thresholds\_by\_primary.R}, whose file names carry the letters the article printed.}

```{r remaining-entries, results="asis"}
walk(which(entries$entry >= 2), function(i) {
  e <- entries[i, ]
  cat("\n\n## ", e$entry, ". ", e$title, "\n\nPublished, ",
      str_remove(e$location, "^published "), ":\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", bold(e$corrected), "\n\n", e$note, "\n", sep = "")
})
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else that
# carries these corrections reads it rather than keeping its own copy, so the two cannot drift.
write_csv(entries, here("errata_entries.csv"))
```
